---
title: "DSA-110 Event Archive"
output:
  html_document:
    theme: cosmo
    include:
      after_body: static/footer.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE,message=FALSE, cache=FALSE)
```

The [DSA-110](https://deepsynoptic.org) is a radio interferometer designed to discover and localize [Fast Radio Bursts](https://en.wikipedia.org/wiki/Fast_radio_burst). The project releases data publicly to support follow-up observations. This page summarizes high-quality, public data sets, including metadata for each event. A low-latency (60 second) alert system is also in development.

## Event table

```{r data-table}
library(tidyverse)
library(DT)
events <- read_csv('events.csv')
events <- transform(events, doi = paste('<a href=https://doi.org/',doi,'>',doi,'</a>',sep=""))
## events <- transform(events, file = paste('<a href=images/',file,'>',file,'</a>',sep=""))
events %>%
  datatable(escape = FALSE,
            rownames = TRUE, 
            colnames = c("Internal Name","MJD","DM","Width","SNR","RA","Dec","PosErr","Notes","DOI"),
            class = "cell-border stripe", 
            caption = "Events",
#            filter = list(position = "bottom"),
            extensions = 'Buttons', options = list(dom = 'Bfrtip',
            buttons = c('colvis', 'csv', 'pdf'))
  )

```

Click on the "DOI" link to view the candidate data, including a summary plot. The search field will filter the table by running a string query on all fields.
 
Column names:

- Internal Name -- Unique internal name generated by the real-time search system. Names begin with an MJD date in <yymmdd> format with a suffix that iterates through four lowercase letters (starting at "aaaa").
- MJD -- Modified Julian Date of event (topocentric at top of band).
- DM -- Dispersion Measure identified by real-time system in pc/cm3.
- Width -- Duration of event (after dedispersion) that produces maximum SNR in real-time search system in milliseconds.
- SNR -- Signal-to-noise-ratio of event measured in a single power beam as a function of time (using Heimdall search code)
- RA -- Right Ascencion (J2000) of peak of localization probability distribution in degrees.
- Dec -- Declination (J2000) of peak of localization probability distribution in degrees.
- PosErr -- Error on localization region in arcseconds.
- Notes -- Human annotations describing the purpose of data set or associations, if known. Examples include: test, pulsar, or a name of a known source.
- DOI -- Unique, persistent URL to public data set, which includes event localization region and dynamic spectrum. Data and DOI are managed by [CaltechDATA](https://data.caltech.edu).
## - PNG file -- Summary plot showing event spectrum, localization, metadata.

